A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-05-07 paper/main.tex
Comment on introduction

\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved => es ist implizit im Text, der von “exact onset \& offsets” und weiter unten von “preliminary annotations” gesprochen wird; keine Ahnung, ob man kommunizieren sollte, dass die preliminary Dinger mal auf github waren; war jedenfalls nicht offensichtlich, beworben o.ä.}

>>>>

\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved => es ist implizit im Text, der von “exact onset \& offsets” und weiter unten von “preliminary annotations” gesprochen wird; keine Ahnung, ob man kommunizieren sollte, dass die preliminary Dinger mal auf github waren; war jedenfalls nicht offensichtlich, beworben o.ä.\\
If you want to take this question in a revision, I am OK with that. However,
the intro still doesn't say anything about WHY one would want to do "modelling of
hemodynamic brain responses correlated with speech-related events" other than
to discard speech as a confound. This seems like a massive underselling.}
